Invasive lionfish present region-wide variation of allometric growth in the Western Atlantic

### 2018-04-09 docs/Manuscript.Rmd
Modified map to include all points

ggplot() +
  geom_sf(data = W) +
  geom_point(data = review[review$Gender == "Both", ], aes(x = lon, y = lat, fill = b, size = N), shape = 21) +
  theme_classic() +
  scale_fill_gradientn(colors = colorRamps::matlab.like(20)) +
  theme(legend.justification = c(0, 1),
        legend.position = c(0, 1),
        legend.background = element_blank()) +
  guides(colorbar = guide_legend(order = 0),
         size = guide_legend(order = 1,
                             direction = "horizontal",
                             title.position = "top")) +
  lims(x = c(-106, -60), y = c(9, 36))
```

>>>>

ggplot() +
  geom_sf(data = W) +
  geom_point(data = review %>%
      mutate(N = ifelse(is.na(N), 1, N)),
    aes(x = lon, y = lat, fill = b, size = N), shape = 21) +
  theme_classic() +
  scale_fill_gradientn(colors = colorRamps::matlab.like(20)) +
  theme(legend.justification = c(0, 1),
        legend.position = c(0, 1),
        legend.background = element_blank()) +
  guides(colorbar = guide_legend(order = 0),
         size = guide_legend(order = 1,
                             direction = "horizontal",
                             title.position = "top")) +
  lims(x = c(-106, -60), y = c(9, 36))
```
